---
title: "Data visualization with ggplot"
author: "Marco Chiapello, PhD"
subtitle: "Based on R-ecology lesson - Data carpentry"
date: "March 29, 2017"
output: 
  beamer_presentation:
    toc: true
    theme: "Boadilla"
    colortheme: "beaver"
    fonttheme: "structuresmallcapsserif"
---

# Importance of data visualization

**Ascomb's quartet**

Use the file example "scraping.R" in Resource directory


# What is ggplot2

* ggplot2 is a plotting system for R, based on the **grammar** **of** **graphics**

* ggplot2 makes **simple** **to** **create** **complex** **plots** from data in a dataframe

* help creating **publication** **quality** **plots** with a **minimal** **amount** **of** **settings** and tweaking

* ggplot graphics are built step by step by **adding** **new** **elements**


# Plotting with ggplot2

To build a ggplot we need to:

* **bind** **the** **plot** to a specific data frame using the data argument

\small
```{r eval=FALSE}
surveys_complete <- read.csv("surveys_complete.csv")
ggplot(data = surveys_complete)
```

\pause

* \normalsize define **aesthetics** (aes), by selecting the variables to be plotted

\small
```{r eval=FALSE}
ggplot(data = surveys_complete,
	   aes(x = weight, y = hindfoot_length))
```


# Plotting with ggplot2

* add **geoms** – graphical representation of the data in the plot 

\small
```{r eval=FALSE}
ggplot(data = surveys_complete,
	aes(x = weight, y = hindfoot_length)) +
  geom_point()
```

\pause 

* \normalsize The **+** in the ggplot2 package is particularly useful because it allows you to modify existing ggplot objects


# Plotting with ggplot2

* Set up plot “templates” and conveniently explore different types of plots

\small
```{r eval=FALSE}
# Create
surveys_plot <- ggplot(data = surveys_complete,
					   aes(x = weight, y = hindfoot_length))

# Draw the plot
surveys_plot + geom_point()
surveys_plot + geom_line()
surveys_plot + geom_count()
surveys_plot + geom_rug()
```
